How to compute the fusion product of MV cycles in type A

### 2021-04-10 draft.tex

@@

\section{Climax}
Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.
% section ??.  
Since $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.

The following result is \cite[Theorem 3.2]{cautis2018categorical} up to transpose.
% 
\begin{theorem} \label{th:TmuWmu}
The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
$$ L \mapsto [t|_{\CC[t]^m/L} ]_{\beta_\mu}' \,. $$
% \acom{Up to transpose?!}
\end{theorem}
%

>>>>

\begin{lemma}
    Let $ T : V \rightarrow V$ be a linear operator on a finite-dimensional complex vector space.   Define a $ \CC[t]$-module structure on $ V $ where $ t $ acts by $ T$.  For any  $ a \in \CC$, the map
    $$ V  \rightarrow V \otimes_{\CC[t]} \cO_a$$
    restricts to an isomorphism between the generalized $ a $ eigenspace of $ T $ and $ V \otimes_{\CC[t]} \cO_a$

    \end{lemma}

\begin{proof}
    Let $ E_b $ denote the generalized $b$-eigenspace of $T$.  Then $ V = \oplus_{b \in \CC} E_b$.  Since $ t - b$ is invertible in $ \cO_a$ and $ T -b $ acts nilpotently on $ E_b$, we see that $ E_b \otimes_{\CC[t]} \cO_a = 0 $.

    So it suffices to show that $ E_a \rightarrow E_a \otimes_{\CC[t]} \cO_a$ is an isomorphism.  By the classification of modules over $ \CC[t]$, it suffices to check this when  $ E_a = \CC[t]/(t-a)^k$, where it is clearly true.
\end{proof}

@@

\section{Climax}
Given $ A \in \TT_\mu$, recall the definition of $ g(A)$ given in \Cref{eq:mvyofa}.  Note that $g(A)t^{-\mu} \in G_1(\Oinf)$.
% section ??.  
Since $ g(A) \in M_n(\CC[t]) \cap G_1(\Oinf)t^\mu$, we will regard $ g(A)$ as giving an element of $ \Grth^+ \cap \cW_\mu$.  (Alternatively, we can see that $ g(A) \CC[t]^m$ satisfies the condition (ii) from Lemma \ref{le:Wmu}.)

The following result is \cite[Theorem 3.2]{cautis2018categorical} up to transpose.
% 
\begin{theorem} \label{th:TmuWmu}
The map $ \TT_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A)\CC[t]^m $ is an isomorphism with inverse given by
$$ L \mapsto [t|_{\CC[t]^m/L} ]^{tr}_{\beta_\mu} \,. $$
%\acom{Up to transpose?!}
\end{theorem}
%
